A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex

With these proxy representations of the concepts for the concept spaces of two
catalogues $C_1$ and $C_2$, we construct a matrix $A$ of inner-products of
super-tf-idf vectors.  Specifically, the matrix elements of $A$ are given by
\begin{align}
A_{ij}(C_1,C_2) = \vec{s}_1(i,C_1) \cdot \vec{s}_1(j,C_2) + \beta \cdot
\vec{s}_2(i,C_1) \cdot \vec{s}_2(j,C_2),
\end{align}
where $i$ is a concept from $C_1$ and $j$ is a concept from $C_2$ and $\beta$ is
the same parameters as before (again, we find $\beta=0.3$ works well).  We may
now use this matrix to transform the vector representation of an item in one
concept space into a vector representation in another concept space.

@@

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$, thus promoting popular items.  In this
context, having defined popularity as the logorithm of node degree reduces the
liklihood that one or two very popular items will always appear as the best
recommendations when using this weighted ranking policy.

>>>>

With these proxy representations of the concepts for the concept spaces of two
catalogues $C_1$ and $C_2$, we construct a matrix $A$ of inner-products of
super-tf-idf vectors.  Specifically, the matrix elements of $A$ are given by
\begin{align}
A_{ij}(C_1,C_2) = \vec{s}_1(i,C_1) \cdot \vec{s}_1(j,C_2) + \beta \cdot
\vec{s}_2(i,C_1) \cdot \vec{s}_2(j,C_2),
\end{align}
where $i$ is a concept from $C_1$ and $j$ is a concept from $C_2$ and $\beta$ is
the same parameter as before (again, we find $\beta=0.3$ works well).  We may
now use this matrix to transform the vector representation of an item in one
concept space into a vector representation in another concept space.

@@

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$, thus promoting popular items.  In this
context, having defined popularity as the logorithm of node degree, instead of
simply node degree, reduces the liklihood that one or two very popular items
will always appear as the best recommendations when using this weighted ranking
policy.
